Trauma treatment delay

### 2023-12-14 lab-book.Rmd
little
code
text

@@

New.subset\$dt_ed_first_ct \<- as.factor(New.subset\$dt_ed_first_ct)

>>>>

as.gt till word

kommentera att best clinical practice är dt inom 30 min. Många får inte
det, bara liten andel får det som största problem

@@

delay over 30/60 mins not always delay, only if bad

OR 1.03 for each step over 0

We can do better for injured and less conscious, clinicians need to be
more aware.
